% !TEX root = ../ac_paper.tex

\subsection*{Acknowledgment}

We would like to thank Anna Beliakova, Michael Douglas, Konstantin Korovin, Alexei Lisitsa, Maksymilian Manko, Ciprian Manolescu, Fabian Ruehle, Josef Urban, and Tony Yue Yu for insightful discussions and comments. We especially want to thank Anna Beliakova for igniting our interest in the Andrews--Curtis conjecture as a framework for exploring problems with long and rare sequences of moves that an RL agent must discover.

The work of A.S. is supported by the US Department of Energy grant DE-SC0010008 to Rutgers University. The authors acknowledge the contributions of Office of Advanced Research Computing (OARC) at Rutgers University for providing access to the Amarel cluster and other computing resources.
A.M.'s work is supported by NSERC grants RES000678 and R7444A03. A.M. also gratefully acknowledges the excellent working conditions provided by the Max Planck Institute for Mathematics in Bonn.
The work of P.K. and B.L. is supported by the SONATA grant no. 2022/47/D/ST2/02058 funded by the Polish National Science Centre. This research was carried out with the support of the Interdisciplinary Centre for Mathematical and Computational Modelling at the University of Warsaw (ICM UW).
The work of S.G. is supported in part by a Simons Collaboration Grant on New Structures in Low-Dimensional Topology, by the NSF grant DMS-2245099, and by the U.S. Department of Energy, Office of Science, Office of High Energy Physics, under Award No. DE-SC0011632.